Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-25 numerical-ppm.tex
One more

Once we have the reconstruction, the primary quantities ($p$, $\rho$, $v$ and $E$) are averaged over the domains corresponding to the three characteristics $C = u-c$, $u$, or $u+c$ (where $c$ is the sound speed in a cell):
\begin{equation}
      q^{C+}_{j+1/2} =
          {1 \over \Delta t C^n_j} \int^{x_{j+1/2}}_{x_{j+1/2}-\Delta t C^n_j} q_j(x) dx
\end{equation}
where $q^{C+}$ refers to the left characteristic $C$ (and a similar integral is done for the right characteristic $q^{C-}$).  The linearized gas dynamics equations are then used to compute second-order accurate left and right states that take into account the multiple wave families.  This process is described in CW84 and we use their equations (3.6) and (3.7).

>>>>

Once we have the reconstruction, the primary quantities ($p$, $\rho$, $v$ and $E$) are averaged over the domains corresponding to the three characteristics $u-c$, $u$, or $u+c$ (where $c$ is the sound speed in a cell).
The linearized gas dynamics equations are then used to compute second-order accurate left and right states that take into account the multiple wave families.  This process is described in CW84 and we use their equations (3.6) and (3.7).
